What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-09 android-stacks.tex
new conclusion v2

>>>>

In this work we present an exploratory study on which we mined the stack 
traces embedded in all issues of Java projects available GitHub, and analyzed the stack traces
reported on a subset of 482 Android projects in more detail. In this study the information extracted 
from stack traces was used in combination with source code and bytecode analysis to 
pin-point patterns of exceptions (mis-)use in Java. And some patterns of exception
(mis)-use were consistently detected such as: unexpected wrappings (e.g., Errors
being wrapped in checked exceptions), revealing that Java hybrid exception
model is not fully used according to its purpose; undocumented runtime
exceptions signaled by third party code (which makes almost impossible for
library clients to protect against such exceptions); and a high prevalence of
java.lang exceptions reported on issues (representing approximately 50\% of the
analyzed issues). Such (mis)uses detected in out study can negatively affect the 
robustness of current Java software systems. Such results shed light to needs for  
 developing tools support to help developers dealing with such problems and 
improving the design of exception handling mechanism in Java.
